### 2017-01-19 papers.tex
Changed paper's index

% =============================================================================
\section{\texttt{IND\_007} - Data Mining Algorithms to Classify Students}

Paper is~\cite{ind_007}. Lists a lot of resources for \gls{dm} in \gls{lms}.

@@

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy;~\cite{ind_008}
    \item Detect students' misuse or game-playing; (2)
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; (34)
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; (9)
    \item Predict/classify students when using intelligent tutoring systems;
        (16)
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural
        networks;~\cite{ind_009}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; (21)
    \item Classifying students using genetic algorithms to predict their final
        grade; (30)
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; (30)
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; (18)
    \item Using neural network models from Moodle logs; (11)
\end{itemize}

@@

% =============================================================================
\section{\texttt{IND\_008} - Discovering Decision Knowledge From Web Log
Portfolio For Managing Classroom Processes By Applying Decision Tree And Data
Cube Technology}

Paper is~\cite{ind_008}. An experiment in which web logs of a \gls{lms} get
analysed in order to find good student behaviour. This paper was found
from~\cite{ind_007}.

@@

% =============================================================================
\section{\texttt{IND\_009} - Predicting Performance From Test Scores Using
Backpropagation and Counterpropagation}

Paper is~\cite{ind_009}. Neural Networks are used to predict students grades
from placement test responses. This paper was found from~\cite{ind_007}.

@@

% =============================================================================
\section{\texttt{IND\_003} - Web Usage Mining for Predicting Final Marks of
Students That Use Moodle Courses}

Paper is~\cite{ind_003}. Paper~\cite{ind_007} is related to this one, for the
authors and experiments in this paper are the same as in~\cite{ind_007}, but
are presented with much more detail.

@@

This paper mines web logs of~\gls{lms} in order to take meaning from them. Like
in~\cite{ind_007} and~\cite{ind_008}, it is asserted that extracting meaningful
information from logs is not trivial, so~\gls{dm} methodologies are used. The
paper makes it so, while presenting the various algorithms testing with
different dataset, having some of which being the results of resampling.

@@

% =============================================================================
\section{\texttt{IND\_010} - Using Educational Data Mining Methods to Study the
Impact of Virtual Classroom in E-Learning}

Paper is~\cite{ind_010}. I haven't seen this paper has a reference of the
previous ones. But found it on Google Scholar while searching for Moodle Data
Mining. The techniques used in this paper are similar to~\cite{ind_008,
ind_003}.

@@

This paper is another~\gls{dm} analysis made to Moodle. Like in previous works,
such as~\cite{ind_008, ind_003}, this paper goes through the process of
pre-processing Moodle data from e-learning courses, applying~\gls{dm}
techniques, and interpreting the results. The objectives of this paper are to
predict student grades given their usage of Moodle in an e-learning
environment.

@@

This paper is very relevant because it displays similar techniques
to~\cite{ind_008, ind_003}. The techniques for pre-processing and mining, the
datasets, and the conclusions are all very similar and will doubtless be very
important as a reference in future work.

@@

% =============================================================================
\section{\texttt{IND\_011} - Predicting students' marks from Moodle logs using
neural network models}

Paper is~\cite{ind_011}. But found it on Google Scholar while searching for
Moodle Data Mining. This is another paper that uses neural networks
like~\cite{ind_009} did.

@@

Another paper that attempts to predict student's success given their usage of
Moodle. In this case we see the usage of neural networks, as we've seen
in~\cite{ind_009}. Like in~\cite{ind_007, ind_008, ind_003, ind_010}, Moodle
logs are processed alongside final grades in order to build features for
students.  Neural networks are then trained using that data.

>>>>

% =============================================================================
\section{\texttt{IND\_001} - Data Mining Algorithms to Classify Students}

Paper is~\cite{ind_001}. Lists a lot of resources for \gls{dm} in \gls{lms}.

@@

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy;~\cite{ind_002}
    \item Detect students' misuse or game-playing; (2)
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; (34)
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; (9)
    \item Predict/classify students when using intelligent tutoring systems;
        (16)
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural
        networks;~\cite{ind_003}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; (21)
    \item Classifying students using genetic algorithms to predict their final
        grade; (30)
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; (30)
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; (18)
    \item Using neural network models from Moodle logs; (11)
\end{itemize}

@@

% =============================================================================
\section{\texttt{IND\_002} - Discovering Decision Knowledge From Web Log
Portfolio For Managing Classroom Processes By Applying Decision Tree And Data
Cube Technology}

Paper is~\cite{ind_002}. An experiment in which web logs of a \gls{lms} get
analysed in order to find good student behaviour. This paper was found
from~\cite{ind_001}.

@@

% =============================================================================
\section{\texttt{IND\_003} - Predicting Performance From Test Scores Using
Backpropagation and Counterpropagation}

Paper is~\cite{ind_003}. Neural Networks are used to predict students grades
from placement test responses. This paper was found from~\cite{ind_001}.

@@

% =============================================================================
\section{\texttt{IND\_004} - Web Usage Mining for Predicting Final Marks of
Students That Use Moodle Courses}

Paper is~\cite{ind_004}. Paper~\cite{ind_001} is related to this one, for the
authors and experiments in this paper are the same as in~\cite{ind_001}, but
are presented with much more detail.

@@

This paper mines web logs of~\gls{lms} in order to take meaning from them. Like
in~\cite{ind_001} and~\cite{ind_002}, it is asserted that extracting meaningful
information from logs is not trivial, so~\gls{dm} methodologies are used. The
paper makes it so, while presenting the various algorithms testing with
different dataset, having some of which being the results of resampling.

@@

% =============================================================================
\section{\texttt{IND\_005} - Using Educational Data Mining Methods to Study the
Impact of Virtual Classroom in E-Learning}

Paper is~\cite{ind_005}. I haven't seen this paper has a reference of the
previous ones. But found it on Google Scholar while searching for Moodle Data
Mining. The techniques used in this paper are similar to~\cite{ind_002,
ind_004}.

@@

This paper is another~\gls{dm} analysis made to Moodle. Like in previous works,
such as~\cite{ind_002, ind_004}, this paper goes through the process of
pre-processing Moodle data from e-learning courses, applying~\gls{dm}
techniques, and interpreting the results. The objectives of this paper are to
predict student grades given their usage of Moodle in an e-learning
environment.

@@

This paper is very relevant because it displays similar techniques
to~\cite{ind_002, ind_004}. The techniques for pre-processing and mining, the
datasets, and the conclusions are all very similar and will doubtless be very
important as a reference in future work.

@@

% =============================================================================
\section{\texttt{IND\_006} - Predicting students' marks from Moodle logs using
neural network models}

Paper is~\cite{ind_006}. But found it on Google Scholar while searching for
Moodle Data Mining. This is another paper that uses neural networks
like~\cite{ind_003} did.

@@

Another paper that attempts to predict student's success given their usage of
Moodle. In this case we see the usage of neural networks, as we've seen
in~\cite{ind_003}. Like in~\cite{ind_001, ind_002, ind_004, ind_005}, Moodle
logs are processed alongside final grades in order to build features for
students.  Neural networks are then trained using that data.
